### 2019-12-13 ic-journal/multivariate.tex
Done, it remains to shorten the proof of TRANS_FV

On the other hand, not every term within the CCS syntax is a context, as 
\hl{context (or equation) variables are not allowed to occur within recursion. The converse
holds however:} if the set of free variables of an CCS term
is disjoint from a list of variables, then the term is indeed a context
w.r.t. the same list of variables:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E}\hfill{[disjoint_imp_context]}
\end{alltt}
On the other hand, for any context (w.r.t.~$\til X$) of the form $\recu Y E$,
the set of free variables of $E$ excluding $Y$ is disjoint with $\til X$:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\hfill{[context_rec]}
\end{alltt}
Note that, in the above lemma we cannot
conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}, because $Y$ as a bound
variable of $\recu Y E$ may also be a free variable in $\til X$. We
also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
it is possible that the bound variable $Y$ occurs with another \hl{nested}
recursion, and then it is free in $E$ (as in $\recu Y
(\recu Z (a.Y + b.Z) + c.Y)$).

@@

With the formal definitions of \multivariate substitution and
\multivariate (weakly guarded) contexts, now we are ready to formally
define \multivariate CCS equations/contractions and their (unique)
solutions. Consider a system of equation $\{X_i = E_i\}_{i\in I}$
(Def.~\ref{def:equation}), or its expanded form (here we suppose $I = [1,n]
\in \mathbb{N}$, i.e.~a finite list):
\begin{equation*}
  \begin{cases}
    &X_1 = E_1[\til X] \\
    &X_2 = E_2[\til X] \\
    & \cdots \\
    &X_n = E_n[\til X]
  \end{cases}
\end{equation*}
Consider its two essential ingredients:
\begin{itemize}
\item $\til X = (X_1, X_2, \ldots, X_n)$: a list of equation variables;
\item $\til E = (E_1, E_2, \ldots, E_n)$: a list of CCS contexts 
  with possible occurrences of free variables in $\til X$.
\end{itemize}
Obviously the two lists must have the same length. 
% The all
% distinctness of $\til X$ is not really necessary but is very
% reasonable. 
Furthermore, we should assume that $\til E$ does not contain
 free variables not in $\til X$.
% , as Milner's unique-solution
% theorems also require the same condition.
% \footnote{One may think that,
%   if all other (i.e.~not in $\til X$) free variables in $\til E$ have
%   the same functionalities as $\nil$ as they are not to be
%   substituted, then all versions of unique-solution
%   theorems should still hold. However this is not the case for at
%   least Milner's Theorem~\ref{t:Mil89s1} as we shall explain.}
The only optional condition we have added is that, for each
$E_i$, the set of its bound variables must be \emph{disjoint} from $\til X$.
% This restriction is actually aligned with literature based on
% process constants as one should never use the same name for equation
% variables and constants. However, we believe this restriction can be
% removed in the future.~
\footnote{Essentially, this condition is due
  to  some early lemmas about \multivariate
  substitutions where \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{BV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}
 appears in the antecedents. Removing this would require 
  more complex proofs.
% (We have succeeded in
%   fixing many such lemmas.) Once all these lemmas are
% fixed, the final unique-solution theorems also do not need this
% disjointness restriction.
} 
Putting all together, below is the fomal
definition of \multivariate CCS equation:
\begin{alltt}
   \HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenEquiv{}}
      \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
      \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
      \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Es}\hfill{[CCS_equation_def]}
\end{alltt}

Now consider (formally) what is a solution $\til P$ of CCS equations. First of
all, the definition should be parametrized on a binary CCS
relation $\R$ such as $\sim$ and $\rcontr$, so that the single definition
could be used for the solution of all kinds of CCS
equations/contractions. Then, of course ${\til P} \ \R\  {\til E}\{\til
P/\til X\}$ must hold, i.e.
\begin{equation*}
  \begin{cases}
    &P_1 \ \R\ E_1\{\til P/\til X\} \\
    &P_2 \ \R\ E_2\{\til P/\til X\} \\
    & \cdots \\
    &P_n \ \R\ E_n\{\til P/\til X\}
  \end{cases}
\end{equation*}
Furthermore, each $P_i$ should be a pure process, i.e. having no free
variable.
% This is usually implicitly assumed in the literature but is
% actually a \emph{must} to complete some unique-solution proofs.
Finally, 
%like the case of CCS equations, we must assume that, 
the set of bound variables %(i.e. process constants) 
must be disjoint from
$\til X$ (this disjointness requirement is optional but makes many proofs
easier). Putting all together,
below is the formal definition of a solution of \multivariate CCS
equations:\footnote{If $R$ is a binary relation of CCS processes,
  \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}} is the same binary relation but for lists of
  CCS processes. Furthermore, \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{A}\\\;\HOLFreeVar{B}} implicitly
  implies that the two lists $A$ and $B$ have the same length.}
\begin{alltt}
   \HOLTokenTurnstile{} \HOLConst{CCS_solution} \HOLFreeVar{R} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}
      \HOLConst{ALL_PROC} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}}
      \HOLConst{LIST_REL} \HOLFreeVar{R} \HOLFreeVar{Ps} \ensuremath{(}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{)}\hfill{[CCS_solution_def]}
\end{alltt}
Note that, in HOL, \HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenEquiv{}}\\\;\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}. The form in the right-hand side suggests that,
\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}} is actually a set containing all
solutions (of \HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}). Then the unique-solution
theorems can be understood thus: any two (syntactically different) elements
in the set are bisimilar.

@@

With the above machinery about \multivariate contexts and substitutions,
the \multivariate case of Lemma~\ref{lem:milner313} is formalised
below:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
       \HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
           \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime}}.
               \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
               \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
               \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}. \HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
\end{alltt}
% Notice that, while Milner did not pointed out explicitly, the involved
% weakly guarded context $E$ must contain free variables up to $\til
% X$~--- the same requirement as in Theorem~\ref{t:Mil89s1}, which
% otherwise does not complete. Besides, we further required that, the
% bound variables of $E$ must be disjoint with $\til X$.

@@

And the \multivariate version of Theorem~\ref{t:rcontraBisimulationU}:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenImp{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Qs}\hfill{[unique_solution_of_rooted_contractions]}
\end{alltt}

Compared with their formal proofs in the \univariate case, although each
step related to \multivariate substitutions is more difficult than
the \univariate case, the entire proofs still follow the same outline,
and many proof scripts can be directly copied from their \univariate version.

>>>>

On the other hand, not every term within the CCS syntax is a context, as 
\hl{context (or equation) variables are not allowed to occur within recursion. The converse
holds however:} if the set of free variables of an CCS term
is disjoint with a list of variables, then the term is indeed a context
w.r.t. the same list of variables:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{context} \HOLFreeVar{Xs} \HOLFreeVar{E}\hfill{[disjoint_imp_context]}
\end{alltt}
On the other hand, for any context (w.r.t.~$\til X$) of the form $\recu Y E$,
the set of free variables of $E$ excluding $Y$ is disjoint with $\til X$:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{(}\HOLConst{rec} \HOLFreeVar{Y} \HOLFreeVar{E}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{FV} \HOLFreeVar{E} \HOLConst{DELETE} \HOLFreeVar{Y}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\hfill{[context_rec]}
\end{alltt}
Note that, in the above lemma we cannot
conclude \HOLinline{\HOLConst{DISJOINT}\\\;\ensuremath{(}\HOLConst{FV}\\\;\HOLFreeVar{E}\ensuremath{)}\\\;\ensuremath{(}\HOLConst{set}\\\;\HOLFreeVar{Xs}\ensuremath{)}}, because $Y$ as a bound
variable of $\recu Y E$ may also be a free variable in $\til X$. We
also cannot conclude \HOLinline{\HOLConst{context}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{E}}, because in $\recu Y E$
it is possible that the bound variable $Y$ occurs with another \hl{nested}
recursion, and then it is free in $E$ (as in $\recu Y
(\recu Z (a.Y + b.Z) + c.Y)$).

@@

With the formal definitions of \multivariate substitution and
\multivariate (weakly guarded) contexts, now we are ready to formally
define \multivariate CCS equations/contractions and their (unique)
solutions. Consider a system of equation $\{X_i = E_i\}_{i\in I}$
(Def.~\ref{def:equation}), or its expanded form (here we suppose $I = [1,n]
\in \mathbb{N}$, i.e.~a finite list):
\begin{equation*}
  \begin{cases}
    &X_1 = E_1[\til X] \\
    &X_2 = E_2[\til X] \\
    & \cdots \\
    &X_n = E_n[\til X]
  \end{cases}
\end{equation*}
Consider its two essential ingredients:
\begin{itemize}
\item $\til X = (X_1, X_2, \ldots, X_n)$: a list of equation variables;
\item $\til E = (E_1, E_2, \ldots, E_n)$: a list of CCS contexts 
  with possible occurrences of free variables in $\til X$.
\end{itemize}
Obviously the two lists $\til X$ and $\til E$ must have the same
length, and in practice the variables in $\til X$ should be all distinct.
Furthermore, we assume that $\til E$ does not contain
 free variables that are not in $\til X$, i.e. each $E_i$ contains
 variables up to $\til X$.
\hl{Finally, the only extraordinary hypothesis} is that, for each
$E_i$, the set of its bound variables must be \emph{disjoint} with
$\til X$. \hl{(In practice, however, one can always
rename all recursion binders in the equations to satisfy this
requirement without changing the semantics of equations.)}
Putting all requirements together, below is the fomal
definition of \multivariate CCS equation:
\begin{alltt}
   \HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenEquiv{}}
      \HOLConst{ALL_DISTINCT} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{LENGTH} \HOLFreeVar{Es} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}}
      \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{FV} \HOLBoundVar{e} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
      \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Es}\hfill{[CCS_equation_def]}
\end{alltt}

Now consider (formally) what is a solution $\til P$ of CCS equations. First of
all, the definition should be parametrized on a binary CCS
relation $\R$ such as $\sim$ and $\rcontr$, so that a single definition
can be used to represent solutions of all kinds of CCS
\hl{equations and inequations.} Then, of course ${\til P} \ \R\  {\til E}\{\til
P/\til X\}$ must hold:
\begin{equation*}
  \begin{cases}
    &P_1 \ \R\ E_1\{\til P/\til X\} \\
    &P_2 \ \R\ E_2\{\til P/\til X\} \\
    & \cdots \\
    &P_n \ \R\ E_n\{\til P/\til X\}
  \end{cases}
\end{equation*}
Furthermore, each $P_i$ should be a pure process, i.e.~having no free
variable.
% This is usually implicitly assumed in the literature but is
% actually a \emph{must} to complete some unique-solution proofs.
Finally, 
%like the case of CCS equations, we must assume that, 
the set of bound variables %(i.e. process constants) 
must be disjoint with
$\til X$ (this disjointness requirement is optional but makes many proofs
easier). Putting all together,
below is the formal definition of a solution of \multivariate CCS
equations:\footnote{If $R$ is a binary relation of CCS processes,
  \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}} is the same binary relation but for lists of
  CCS processes. Furthermore, \HOLinline{\HOLConst{LIST_REL}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{A}\\\;\HOLFreeVar{B}} implicitly
  implies that the two lists $A$ and $B$ have the same length.}
\begin{alltt}
   \HOLTokenTurnstile{} \HOLConst{CCS_solution} \HOLFreeVar{R} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenEquiv{}}
      \HOLConst{ALL_PROC} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}} \HOLConst{EVERY} \ensuremath{(}\HOLTokenLambda{}\HOLBoundVar{e}. \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLBoundVar{e}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)}\ensuremath{)} \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenConj{}}
      \HOLConst{LIST_REL} \HOLFreeVar{R} \HOLFreeVar{Ps} \ensuremath{(}\HOLConst{MAP} \ensuremath{[}\HOLFreeVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{Es}\ensuremath{)}\hfill{[CCS_solution_def]}
\end{alltt}
Note that, in HOL, the two logical terms ``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}\\\;\HOLFreeVar{Ps}}'' and ``\HOLinline{\HOLFreeVar{Ps}\\\;\HOLSymConst{\HOLTokenIn{}}\\\;\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' have the same meaning
(w.r.t.~\texttt{pred_set} theory). The latter form suggests that,
``\HOLinline{\HOLConst{CCS_solution}\\\;\HOLFreeVar{R}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}'' is actually a set containing all
solutions (of ``\HOLinline{\HOLConst{CCS_equation}\\\;\HOLFreeVar{Xs}\\\;\HOLFreeVar{Es}}''). Then the unique-solution
theorems can be understood in this way: any two (syntactically different) elements
in the set are bisimilar.

@@

With all above machineries of \multivariate contexts and substitutions,
the \multivariate case of Lemma~\ref{lem:milner313} is formalised below:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{E} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \HOLFreeVar{E} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \HOLFreeVar{E}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenImp{}}
   \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Ps}.
       \HOLConst{LENGTH} \HOLBoundVar{Ps} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}}
       \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{u} \ensuremath{\HOLBoundVar{P}\sp{\prime}}.
           \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\HOLTokenImp{}}
           \HOLSymConst{\HOLTokenExists{}}\ensuremath{\HOLBoundVar{E}\sp{\prime}}.
               \HOLConst{context} \HOLFreeVar{Xs} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}} \HOLConst{FV} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenSubset{}} \HOLConst{set} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenConj{}} \HOLConst{DISJOINT} \ensuremath{(}\HOLConst{BV} \ensuremath{\HOLBoundVar{E}\sp{\prime}}\ensuremath{)} \ensuremath{(}\HOLConst{set} \HOLFreeVar{Xs}\ensuremath{)} \HOLSymConst{\HOLTokenConj{}}
               \ensuremath{\HOLBoundVar{P}\sp{\prime}} \HOLSymConst{\ensuremath{=}} \ensuremath{[}\HOLBoundVar{Ps}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}} \HOLSymConst{\HOLTokenConj{}}
               \HOLSymConst{\HOLTokenForall{}}\HOLBoundVar{Qs}. \HOLConst{LENGTH} \HOLBoundVar{Qs} \HOLSymConst{\ensuremath{=}} \HOLConst{LENGTH} \HOLFreeVar{Xs} \HOLSymConst{\HOLTokenImp{}} \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \HOLFreeVar{E} \HOLTokenTransBegin\HOLBoundVar{u}\HOLTokenTransEnd \ensuremath{[}\HOLBoundVar{Qs}\ensuremath{/}\HOLFreeVar{Xs}\ensuremath{]} \ensuremath{\HOLBoundVar{E}\sp{\prime}}
\end{alltt}
% Notice that, while Milner did not pointed out explicitly, the involved
% weakly guarded context $E$ must contain free variables up to $\til
% X$~--- the same requirement as in Theorem~\ref{t:Mil89s1}, which
% otherwise does not complete. Besides, we further required that, the
% bound variables of $E$ must be disjoint with $\til X$.

@@

\hl{So is} the \multivariate version of Theorem~\ref{t:rcontraBisimulationU}:
\begin{alltt}
\HOLTokenTurnstile{} \HOLConst{CCS_equation} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}} \HOLConst{weakly_guarded} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenConj{}}
   \HOLFreeVar{Qs} \HOLSymConst{\HOLTokenIn{}} \HOLConst{CCS_solution} \HOLConst{OBS_contracts} \HOLFreeVar{Xs} \HOLFreeVar{Es} \HOLSymConst{\HOLTokenImp{}}
   \HOLFreeVar{Ps} \HOLSymConst{\HOLTokenObsCongr} \HOLFreeVar{Qs}\hfill{[unique_solution_of_rooted_contractions]}
\end{alltt}

Compared with their formal proofs in the \univariate case, although each
step related to \multivariate substitutions is more difficult than
the \univariate case, the entire proofs still follow the same \hl{outlines}.
and many proof \hl{steps} can even be copied from their \univariate \hl{companions}.
